\textbf{A Serious Game for Aiding the Screening of Dyslexia in Children and Young Adults}

### 2014-06-24 article.tex
Add Initial Screening Task Descriptions

>>>>

\subsubsection{Visual Sequential Memory} 
Based on the work conducted in \cite{sequential}, for this screening task users are presented with a symbol sequence and must select the matching sequence from a set of similar sequences. In order for this to test memory, the target sequence and possible matches must not be on screen at the time. The time taken and number of errors made are recorded as metrics, as well as the number of times the user switches between viewing the target sequence and the possible matches.
\cite{sequential} suggests that those with dyslexia are likely to perform worse than controls on this task.

\subsubsection{Visual Memory}
Visual memory is tested by presenting the user with an elevator floor number they must travel too and asking them to select that number from a set of similar numbers, again the target number and possible matches are not presented at the same time. Research suggested that those with dyslexia struggle to remember of the shapes of words and numbers, this task is designed to utilise that. It is expected that those with dyslexia will perform worse than controls on this task, when considering time taken and number of errors made.
